Network Configuration Synthesis with Abstract Topologies

### 2016-11-10 paper/abstraction/paper.tex
updating appendix with new definitions

\newcommand{\Con}{\text{con}}

\vspace{2em}
\begin{figure*}[t!]\small

  \hrulefill%
  \vspace{1em}

  \begin{minipage}[t]{.46\linewidth}
  \hdr{ABGP Syntax}{}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{rclr}
     abgp &::=& l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k & \textit{abgp policy} \\
     rc   &::=& t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k & \textit{router config} \\
     pc   &::=& ma_1, \dots, ma_k & \textit{prefix config} \\
     ma   &::=& lp : ({ns}_1, c_1) \rightarrow ({ns}_2, c_2) & \textit{match action} \\
     ns   &::=& \{ l_1, ~\dots,~ l_k \} & \textit{peers} \\
     t    &::=& \$x \BNFALT d.d.d.d/[d..d] & \textit{predicate} \\
     c    &   & & \textit{community value} \\
     lp   &   & & \textit{local preference} \\
  \end{array} \]%

  \end{minipage}
  %
  %
  \begin{minipage}[t]{.5\linewidth}
  \hdr{Compilation}{}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{l}
     \text{compile}_\text{ABGP}( (t_1,PG_1,ord_1), \dots, (t_k,PG_k,ord_k), G ) = \\
     ~~~~~ \{ l \rightarrow rc ~\vert~ \\
     ~~~~~~~~~ l \in internal(G.V), \\
     ~~~~~~~~~ rc = \bigcup_i~ \{ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ m = (l,q_m) \in PG_i, \\
     ~~~~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_n) \in \text{adjIn}(PG_i,m) \} \\
     ~~~~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_i,m) \} \\
     ~~~~~~~~~~~~~~~~~~~~~ ma_j = ord_i(m) : (in,q_n) \rightarrow (out,q_m) \} \} \\
     \\
     \text{compile}( p_1, \dots, p_k, G) = \\
     ~~~~~~ \text{compile}_\text{ABGP}(\text{compile}_\text{PG}(p_1,G), \dots, \text{compile}_\text{PG}(p_k,G)) \\
  \end{array} \]%
  \end{minipage}

  \vspace{1em}
  \vspace{1em}

  \vspace*{-2\baselineskip}
  \begin{minipage}[t]{\linewidth}
  \hdr{Policy Concretization}{}
  \vspace*{-2\baselineskip}
  %
  \[ \begin{array}{lcl}
     \\
     \Con(\emptyset, \Gamma, f)      &=& \emptyset \\
     \Con(l, \Gamma, f)              &=& \Sigma ~ f^{-1}(l) \\
     \Con(r_1 \cup r_2, \Gamma, f)   &=& \Con(r_1,\Gamma,f) \cup \Con(r_2,\Gamma,f) \\
     \Con(r_1 \cap r_2, \Gamma, f)   &=& \Con(r_1,\Gamma,f) \cap \Con(r_2,\Gamma,f) \\
     \Con(!r, \Gamma, f)             &=& !\Con(r,\Gamma,f) \\
     \Con(r^*, \Gamma, f)            &=& \Con(r,\Gamma,f)^* \\

     \Con(pfx ~\Path~ r_1, ~\dots~, r_k, \Gamma, f) &=&
          pfx ~\Path~ \Con(r_1,\Gamma,f), ~\dots~, \Con(r_k,\Gamma,f)  \\

     \Con(\$x ~\Path~ r_1, ~\dots~, r_k, \Gamma, f) &=&

         \{ pfx ~\Path~ \Con(r_1,\Gamma,f) \cap \text{end}(l), ~\dots~,
           \Con(r_k,\Gamma,f) \cap \text{end}(l) ~\vert~ (pfx,l) \in \Gamma(x) \}  \\

     \Con(p_1, \dots, p_n, \Gamma,f) &=& \Con(p_1, \Gamma,f), \dots, \Con(p_n, \Gamma,f) \\

  \end{array} \]%
  \end{minipage}

  \vspace{1em}
  \vspace{1em}

  \begin{minipage}[t]{\linewidth}
  \hdr{ABGP Concretization}{}
  \vspace*{-2\baselineskip}
  %
  \[ \begin{array}{lcl}
     \\
     \Con(l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k,\Gamma,f,G)
        & = &
        \bigcup_i~ \{ \ell \rightarrow con(rc_i,\ell,\Gamma,f,G)  ~\vert~ \ell \in f^{-1}(l_i) \}
        \\
     \Con(t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k,\ell,\Gamma,f,G)
        & = &
        \Con(t_1 \rightarrow {pc}_1,\ell,\Gamma,f,G), \dots, \Con(t_k \rightarrow {pc}_k,\ell,\Gamma,f,G)
        \\
     \Con(pfx \rightarrow {pc},\ell,\Gamma,f,G)
        & = &
        pfx \rightarrow \Con(pc,\text{true},\ell,\Gamma,f,G)
        \\
     \Con(\$x \rightarrow {pc},\ell,\Gamma,f,G)
        & = &
        \{ pfx \rightarrow \Con(pc, l=\ell, \ell,\Gamma,f,G) ~\vert~ (pfx, l) \in \Gamma(x) \}
        \\
     \Con(ma_1, \dots, ma_k,o,\ell,\Gamma,f,G)
        & = &
        \Con(ma_1,o,\ell,\Gamma,f,G), \dots, \Con(ma_k,o,\ell,\Gamma,f,G)
        \\

     \Con(n_1 : ({ns}_1, n_2) \rightarrow ({ns}_2, n_3),o,\ell,\Gamma,f,G)
        & = & \textbf{if}~ ns_1 = \{\text{start}\} ~\text{and}~ o = \text{false} ~\textbf{then}~ \bullet \\
        &   & \textbf{else}~ n_1 : ( \Con({ns}_1,\ell,\Gamma,f,G), n_2) \rightarrow (\Con({ns}_2,\ell,\Gamma,f,G),n_3)

        \\
     \Con(\{ l_1, ~\dots,~ l_k \}, \ell, \Gamma,f,G)
        & = &
        \bigcup_i ~ \{ x ~\vert~ x \in f^{-1}(l_i),~ (x,\ell) \in G.E \}
        \\
  \end{array} \]%
  \end{minipage}

  \vspace{1em}
  \hrulefill%
  \vspace{1em}

  \caption{ABGP syntax, compilation from product graphs, policy concretization, and ABGP concretization.}
  \label{fig:concretization}
\end{figure*}%

@@

\para{ABGP language}

We introduct a simple language for BGP configurations called ABGP. Figure~\ref{fig:concretization} shows the syntax for an ABGP policy. An ABGP policy maps topology locations $l$ to router configurations $rc$. Each router configuration $rc$ is a sequence of predicates $t$ and their corresponding configuration $pc$. A prefix configuration $pc$ is a sequence of match actions. Each match action $ma$ consists of a preference value $d_1$, followed by a set of imports from neighbors $ns_1$ and community value (\IE, state of the product graph) $d_2$ expected from those neighbors, as well as export neighbors $ns_2$ and the community value $d_3$ to attach before sending to those neighbors.

\para{Compilation}

Figure~\ref{fig:concretization} defines compilation from a \sysname policy to an ABGP policy. It starts by compiling ($\text{compile}_\text{PG}$) separately each constraint of the form $p_i = (t_i ~\Path~ r_{i1} ~\Prefer~ r_{ik})$ to a product graph $PG = (G', s, P)$. The function $\text{compile}_\text{PG}$ returns the test $t_i$, product graph $PG_i$, and the preference ordering $ord_i$.
%
The function $\text{compile}_\text{ABGP}$ then takes a sequence of tuples $(t_i, PG_i, ord_i)$ and returns an ABGP policy. For each internal router, it looks at each set of neighbor with the same community state $q_n$ and matches any of those neighbors with the preference provided by the ordering $ord$. It then exports this advertisement to each adjacent peer along an outgoing edge and adds the community value for the current state $q_m$.

%We assume a particular router $l$ appears at most once in any abgp specification.
We build configs using set-builder notation.  For instance,
$\{l \rightarrow rc ~\vert~ l \in V \wedge p(l,rc)\}$ denotes the abgp policy
%
\[ \begin{array}{c}
  l_1 \rightarrow rc_{1},... \\
  ...           \\
  l_k \rightarrow rc_{k},... \\
\end{array} \]

where $l_1, ..., l_k$ are the nodes in the topology
and each $rc_{i}$ satisfies $p(l_i,rc_{i})$. We also use the $\bigcup$ operator to denote sequence concatenation.

\para{Concretization}

Concretization for a \sysname policy takes as input, the policy and a context
$\Gamma : Var \rightarrow 2^{Prefix \times V}$,
which maps from a template prefix to a set of pairs of a concrete prefix and a concrete location that "owns" the prefix.
%
For each regular expression $r$, we replace each abstract location with the sum over its corresponding concrete locations under the inverse homomorphism $f^{-1}$. For each template variable, we replace it with a new entry for each of its corresponding concrete prefixes under the supplied mapping $\Gamma$. We also intersect the resulting concretized regular expression with $\text{end}(l)$ to capture the fact that this traffic is owned by the concrete location $l$.

We also define concretization over the ABGP policy in a similar manner. We replace each abstract router configuration $l \rightarrow rc$ a new entry for each concrete location $\ell \in f^{-1}(l)$. The concrete location $\ell$ is passed as a parameter to $con$ to remember the current router.
%
To concretize a prefix policy with a template ($\$x \rightarrow pc$) we replace it with a sequence of policies, one for each prefix in context ($(pfx,l) \in \Gamma(x)$). Match action statements where the set of import neighbors is the singleton set containing the product graph start node $\{ start \}$ and we are not currently at looking at the router configuration for the location specified in the context $l$, then we drop the match action. This is denoted with the $\bullet$ symbol. Finally, to concretize a set of neighbors, we again use $f^{-1}$ to find the set of concrete neighbors under the inverse homomorphism, but then restrict it to those that are actually connected in the underlying concrete topology with $G.E$.

>>>>

\newcommand{\Con}{\text{con}}
\newcommand{\Pfx}{\mathit{pfx}}%

%\vspace{2em}
%\begin{figure*}[t!]\small%

%  \hrulefill%
%  \vspace{1em}%

%  \begin{minipage}[t]{.46\linewidth}
%  \hdr{ABGP Syntax}{}
%  \vspace*{-1\baselineskip}
%  %
%  \[ \begin{array}{rclr}
%     d    &   & & \textit{integer} \\
%     c    &   & & \textit{community} \\
%     t    &::=& \$x \BNFALT d.d.d.d/[d..d] & \textit{predicate} \\
%     ns   &::=& \{ l_1, ~\dots,~ l_k \} & \textit{peers} \\
%     ma   &::=& d : ({ns}_1, c_1) \rightarrow ({ns}_2, c_2) & \textit{match action} \\
%     pc   &::=& ma_1, \dots, ma_k & \textit{prefix config} \\
%     rc   &::=& t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k & \textit{router config} \\
%     abgp &::=& l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k & \textit{abgp policy} \\%

%  \end{array} \]%%

%  \end{minipage}
%  %
%  %
%  \begin{minipage}[t]{.5\linewidth}
%  \hdr{Compilation}{}
%  \vspace*{-1\baselineskip}
%  %
%  \[ \begin{array}{l}
%     \text{compile}_\text{ABGP}( (t_1,PG_1,ord_1), \dots, (t_k,PG_k,ord_k), G ) = \\
%     ~~~~~ [~ l \rightarrow rc ~\vert~ \\
%     ~~~~~~~~~ l \in internal(G.V), \\
%     ~~~~~~~~~ rc = \mathit{append}_i~  \\
%     ~~~~~~~~~~~~~~~ [~ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
%     ~~~~~~~~~~~~~~~~~~~~~ m = (l,q_m) \in PG_i, \\
%     ~~~~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG_i,m), \\
%     ~~~~~~~~~~~~~~~~~~~~~ (in,q_n) = \{ (bs,q_n) ~\vert~ (\_,q_n) \in pin, bs=\{b ~\vert~ (b,q_n) \in pin \} \} \\
%     ~~~~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_i,m) \} \\
%     ~~~~~~~~~~~~~~~~~~~~~ ma_j = ord_i(m) : (in,q_n) \rightarrow (out,q_m) ~] ~] \\
%     \\
%     \text{compile}( p_1, \dots, p_k, G) = \\
%     ~~~~~~ \text{compile}_\text{ABGP}(\text{compile}_\text{PG}(p_1,G), \dots, \text{compile}_\text{PG}(p_k,G), G) \\
%  \end{array} \]%
%  \end{minipage}%

%  \vspace{1em}
%  \vspace{1em}%

%  \vspace*{-2\baselineskip}
%  \begin{minipage}[t]{1.01\linewidth}
%  \hdr{Policy Concretization}{}
%  \vspace*{-2\baselineskip}
%  %
%  \[ \begin{array}{lcl}
%     \\
%     \Con(\emptyset, \Gamma, f)      &=& \emptyset \\
%     \Con(l, \Gamma, f)              &=& \Sigma_i ~ f_i^{-1}(l) \\
%     \Con(r_1 \cup r_2, \Gamma, f)   &=& \Con(r_1,\Gamma,f) \cup \Con(r_2,\Gamma,f) \\
%     \Con(r_1 \cap r_2, \Gamma, f)   &=& \Con(r_1,\Gamma,f) \cap \Con(r_2,\Gamma,f) \\
%     \Con(!r, \Gamma, f)             &=& !\Con(r,\Gamma,f) \\
%     \Con(r^*, \Gamma, f)            &=& \Con(r,\Gamma,f)^* \\%

%     \Con(\Pfx ~\Path~ r_1, ~\dots~, r_k, \Gamma, f) &=&
%          \Pfx ~\Path~ \Con(r_1,\Gamma,f), ~\dots~, \Con(r_k,\Gamma,f)  \\%

%     \Con(\$x ~\Path~ r_1, ~\dots~, r_k, \Gamma, f) &=&%

%         [~ \Pfx ~\Path~ \Con(r_1,\Gamma,f) \cap \text{end}(l), ~\dots~, \\%

%         & & ~~~~~~~~~~~~~~~ \Con(r_k,\Gamma,f) \cap \text{end}(l) ~\vert~ (\Pfx,l) \in \Gamma(x) ~]  \\%

%     \Con(p_1, \dots, p_n, \Gamma,f) &=& \Con(p_1, \Gamma,f), \dots, \Con(p_n, \Gamma,f) \\%

%  \end{array} \]%
%  \end{minipage}%

%  \vspace{1em}
%  \vspace{1em}%

%  \begin{minipage}[t]{\linewidth}
%  \hdr{ABGP Concretization}{}
%  \vspace*{-2\baselineskip}
%  %
%  \[ \begin{array}{lcl}
%     \\
%     \Con(l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k,\Gamma,f,G)
%        & = &
%        \mathit{append}_i~ [~ \ell \rightarrow con(rc_i,\ell,\Gamma,f,G)  ~\vert~ \ell \in f^{-1}(l_i) ~]
%        \\
%     \Con(t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k,\ell,\Gamma,f,G)
%        & = &
%        \Con(t_1 \rightarrow {pc}_1,\ell,\Gamma,f,G), \dots, \Con(t_k \rightarrow {pc}_k,\ell,\Gamma,f,G)
%        \\
%     \Con(\Pfx \rightarrow {pc},\ell,\Gamma,f,G)
%        & = &
%        \Pfx \rightarrow \Con(pc,\text{true},\ell,\Gamma,f,G)
%        \\
%     \Con(\$x \rightarrow {pc},\ell,\Gamma,f,G)
%        & = &
%        [~ \Pfx \rightarrow \Con(pc, l=\ell, \ell,\Gamma,f,G) ~\vert~ (\Pfx, l) \in \Gamma(x) ~]
%        \\
%     \Con(ma_1, \dots, ma_k,o,\ell,\Gamma,f,G)
%        & = &
%        \Con(ma_1,o,\ell,\Gamma,f,G), \dots, \Con(ma_k,o,\ell,\Gamma,f,G)
%        \\%

%     \Con(n_1 : ({ns}_1, n_2) \rightarrow ({ns}_2, n_3),o,\ell,\Gamma,f,G)
%        & = & \textbf{if}~ ns_1 = \{\text{start}\} ~\text{and}~ o = \text{false} ~\textbf{then}~ \bullet \\
%        &   & \textbf{else}~ n_1 : ( \Con({ns}_1,\ell,\Gamma,f,G), n_2) \rightarrow (\Con({ns}_2,\ell,\Gamma,f,G),n_3)%

%        \\
%     \Con(\{ l_1, ~\dots,~ l_k \}, \ell, \Gamma,f,G)
%        & = &
%        \bigcup_i ~ \{ x ~\vert~ x \in f^{-1}(l_i),~ (x,\ell) \in G.E \}
%        \\
%  \end{array} \]%
%  \end{minipage}%

%  \vspace{1em}
%  \hrulefill%
%  \vspace{1em}%

%  \caption{ABGP syntax, compilation from product graphs, policy concretization, and ABGP concretization.}
%  \label{fig:concretization}
%\end{figure*}%

@@

%\para{ABGP language}%

%We introduct a simple language for BGP configurations called ABGP. Figure~\ref{fig:concretization} shows the syntax for an ABGP policy. An ABGP policy maps topology locations $l$ to router configurations $rc$. Each router configuration $rc$ is a sequence of predicates $t$ and their corresponding configuration $pc$. A prefix configuration $pc$ is a sequence of match actions. Each match action $ma$ consists of a preference value $d_1$, followed by a set of imports from neighbors $ns_1$ and community value (\IE, state of the product graph) $d_2$ expected from those neighbors, as well as export neighbors $ns_2$ and the community value $d_3$ to attach before sending to those neighbors.%
%

%\para{Compilation}%

%Figure~\ref{fig:concretization} defines compilation from a \sysname policy to an ABGP policy. It starts by compiling ($\text{compile}_\text{PG}$) separately each constraint of the form $p_i = (t_i ~\Path~ r_{i1} ~\Prefer~ r_{ik})$ to a product graph $PG = (G', s, P)$. The function $\text{compile}_\text{PG}$ returns the test $t_i$, product graph $PG_i$, and the preference ordering $ord_i$.
%%
%The function $\text{compile}_\text{ABGP}$ then takes a sequence of tuples $(t_i, PG_i, ord_i)$ and returns an ABGP policy. For each internal router, it looks at each set of neighbor with the same community state $q_n$ and matches any of those neighbors with the preference provided by the ordering $ord$. It then exports this advertisement to each adjacent peer along an outgoing edge and adds the community value for the current state $q_m$.%

%%We assume a particular router $l$ appears at most once in any abgp specification.
%We build configs using set-builder notation.  For instance,
%$\{l \rightarrow rc ~\vert~ l \in V \wedge p(l,rc)\}$ denotes the abgp policy
%%
%\[ \begin{array}{c}
%  l_1 \rightarrow rc_{1},... \\
%  ...           \\
%  l_k \rightarrow rc_{k},... \\
%\end{array} \]

%where $l_1, ..., l_k$ are the nodes in the topology
%and each $rc_{i}$ satisfies $p(l_i,rc_{i})$. We also use the $\bigcup$ operator to denote sequence concatenation.%

%\para{Concretization}%

%Concretization for a \sysname policy takes as input, the policy and a context
%$\Gamma : Var \rightarrow 2^{Prefix \times V}$,
%which maps from a template prefix to a set of pairs of a concrete prefix and a concrete location that "owns" the prefix.
%%
%For each regular expression $r$, we replace each abstract location with the sum over its corresponding concrete locations under the inverse homomorphism $f^{-1}$. For each template variable, we replace it with a new entry for each of its corresponding concrete prefixes under the supplied mapping $\Gamma$. We also intersect the resulting concretized regular expression with $\text{end}(l)$ to capture the fact that this traffic is owned by the concrete location $l$.%

%We also define concretization over the ABGP policy in a similar manner. We replace each abstract router configuration $l \rightarrow rc$ a new entry for each concrete location $\ell \in f^{-1}(l)$. The concrete location $\ell$ is passed as a parameter to $con$ to remember the current router.
%%
%To concretize a prefix policy with a template ($\$x \rightarrow pc$) we replace it with a sequence of policies, one for each prefix in context ($(pfx,l) \in \Gamma(x)$). Match action statements where the set of import neighbors is the singleton set containing the product graph start node $\{ start \}$ and we are not currently at looking at the router configuration for the location specified in the context $l$, then we drop the match action. This is denoted with the $\bullet$ symbol. Finally, to concretize a set of neighbors, we again use $f^{-1}$ to find the set of concrete neighbors under the inverse homomorphism, but then restrict it to those that are actually connected in the underlying concrete topology with $G.E$.
